{\fontfamily{ptm}\selectfont Lorum ipsum}

### 2025-07-03 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

>>>>

        Hi Arron would you like to add me for the co-authorship to continue this line of work and see how Nesterov's Accelerated Technique may work out for the stochastic gradient method? 
        These results are solid results but they are still partial results and, below are the potential I foresee for this these ideas. 
        \begin{enumerate}
            \item Narrow down the sequence $\alpha_k$ and make sure that it can allow the quantity: 
                \mathbb E_k\left[
            is negative, or at least bounded. I am not sure how this will work out, but I have some solid ideas aroud it. 
            \item Roll up the inequality in Theorem \ref{thm:snapg2-one-step} recursively and, determine the convergence rate through $\alpha_k$ that makes the previous item true. 
            In addition, I have the hunches that the convergence reate involves the variance of $\mu^{(I_k)}$ and, it will slower than the non-stochastic case of the algorithm. 
        \end{enumerate}
        For the future we can: 
        \begin{enumerate}
            \item Extend the definition of strong convexity to quasi-norm. 
            \item Show the convergence of the method for objective function that is not necessarily strong convex, but quasi-strongly convex. This is a much weaker assumption it works well in practice for well known problems.  
        \end{enumerate}
